---
title: "RcppSimdJson Notes"
output:
    github_document:
        toc: true
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(width = 100)
```


```{r}
library(RcppSimdJson)
```

# 2020-08-08

... via experimental/pointer

## Enhancements

### Better Queries

We can still pass a single `query=` that's applied to each `json=` element.

```{r}
json_to_query <- c(json1 = '["a",{"b":{"c": [[1,2,3],[4,5,6]]}}]',
                   json2 = '["a",{"b":{"c": [[7,8,9],[10,11,12]],"d":[[13,14,15,16],[17,18,19,20]]}}]')
#                                                                 ^^^ json1 doesn't have "d"
```


```{r}
fparse(json_to_query, query = "1/b/c")
```

But now we can also pass multiple "flat" queries (a named or unnamed character vector). Each element of `query=` is applied to all elements of `json=`.

This is the preferred method if each `json=` has roughly the same schema and we want to extract the same data from each of them.

```{r}
fparse(json_to_query, query = c(query1 = "1/b/c",
                                query2 = "1/b/c/0",
                                query3 = "1/b/c/1"))
```

When we want to extract different data from each `json=`, such as when the schemata aren't related, we can also specify a "nested" query. This is a list of character vectors that are applied in a zip-like fashion. 

```{r}
fparse(json_to_query,
       query = list(queries1 = c(c1 = "1/b/c/0",
                                 c2 = "1/b/c/1"),
                    queries2 = c(d1 = "1/b/d/0",
                                 d2 = "1/b/d/1")))
```

### Compressed Files

We now handle .gz, .bz2, and .xz files that are decompressed to a raw vector (via `memDecompress()`).

```{r}
.read_compress_write_load <- function(file_path, temp_dir) {
    types <- c("gzip", "bzip2", "xz")
    exts <- c("gz",    "bz2",   "xz")

    init <- readBin(file_path, n = file.size(file_path), what = "raw")
    
    mapply(function(type, ext) {
        target_path <- paste0(temp_dir, "/", basename(file_path), ".", ext)
        writeBin(memCompress(init, type = type), target_path)
        RcppSimdJson::fload(target_path)
    }, types, exts, SIMPLIFY = FALSE)
}

my_temp_dir <- sprintf("%s/rcppsimdjson-compressed-files", tempdir())
dir.create(my_temp_dir)
all_files <- dir(
    system.file("jsonexamples", package = "RcppSimdJson"),
    recursive = TRUE,
    pattern = "\\.json$",
    full.names = TRUE
)
names(all_files) <- basename(all_files)
res <- t(sapply(all_files, .read_compress_write_load, my_temp_dir))
unlink(my_temp_dir)

stopifnot(all(apply(
    res, 1L, 
    function(.x) identical(.x[[1]], .x[[2]]) && 
        identical(.x[[1]], .x[[3]])
)))

res
```


### Smarter URL Handling

With compressed files supported, we can better leverage the `compressed_download=` parameter. 

Additionally, remote JSON files are now downloaded simultaneously `if (getOption("download.file.method", default = "auto") == "libcurl")`.


```{r}
json_urls <- c(
    "https://raw.githubusercontent.com/eddelbuettel/rcppsimdjson/master/inst/jsonexamples/small/smalldemo.json",
    "https://raw.githubusercontent.com/eddelbuettel/rcppsimdjson/master/inst/jsonexamples/small/demo.json"
)
```



```{r}
my_temp_dir <- sprintf("%s/rcppsimdjson-downloads", tempdir())
dir.create(my_temp_dir)

fload(json_urls,
      query = list(c(width = "Thumbnail/Width", 
                     height = "Thumbnail/Height"),
                   c(width = "Image/Thumbnail/Width", 
                     height = "Image/Thumbnail/Height")),
      temp_dir = my_temp_dir,
      keep_temp_files = TRUE,
      compressed_download = TRUE)

list.files(my_temp_dir)
```

## Fixes

### Lurking Windows String Encoding Trap

Windows was mangling non-ASCII UTF-8.

The issue/fix are essentially the same as https://github.com/SymbolixAU/jsonify/pull/57 and there's now a test using a mix of 1-4 byte characters.

```{r}
extended_unicode <- '"լ ⿕  ٷ 豈 ٸ 㐀 ٹ 丂 Ɗ 一 á ٵ ̝ ѵ ̇ ˥ ɳ Ѡ · վ  й ף ޑ  ц Ґ  ӎ Љ ß ϧ ͎ ƽ ޜ է ϖ y Î վ Ο Ӊ ٻ ʡ ө ȭ ˅ ޠ ɧ ɻ ث ́ ܇ ܧ ɽ Ո 戸 Ð 坮 ٳ 䔢 찅 곂 묨 ß ᇂ ƻ 䏐 ܄ 㿕 ս ّ 昩 僫 똠 Ɯ ٰ É"'
fparse(extended_unicode)
fparse(charToRaw(extended_unicode))
```

